opponent modelling

### 2020-01-15 exp1_clean_analysis.Rmd
finalise v1 of report

```{r}
dat <- read.csv("data20180719.csv")
```

@@

# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- factor(as.numeric(cut(dat$round,2)),labels =c("first half", "second half"))

# create a new variable "game.f" as a factor variable of games
dat$game.f <- factor(dat$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))

# overall score to pay bonuses 
dat_score <- dat %>% 
  group_by(human_id) %>% 
      summarize(overall_score = sum(score))
(avg_bonus <- floor(mean(abs(dat_score$overall_score))))*0.02

#Group data by human_id and calculate mean score per block of each game.
dat2 <- dat %>% 
  group_by(human_id,condition,game,block,game.f) %>% 
      summarize(block_score = mean(score))

@@

dat_26 <- subset(dat,round >1 & round <7, drop =TRUE)
dat2_6 <- dat_26 %>% 
  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
      summarise(early_score = mean(score))

# Check group means and SDs
group_by(dat2_6, game.f) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
group_by(dat2_6, game.f,condition) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
# plot scores per game 
ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

@@

# including confidence

aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
summary(aov_conf_26)

(ls4 <- lsmeans(aov_early, "game.f"))
(summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))

(means.int2 <- lsmeans(aov_early, specs = c("game.f","condition")))
(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","NUM")))
(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))

@@

# plots overall effect by game :
ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f",palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))

@@

```{r}
# adding confidence and difficulty feedback 
datcd <- dat %>% 
  group_by(human_id,condition,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))

@@

```{r}
# ANCOVA with confidence as covariate 
dat_ancova <- dat %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))
# Centering variables for ANCOVA 
dat_ancova$conf_cen <- scale(dat_ancova$confidence, center=TRUE, scale=FALSE) 
dat_ancova$diff_cen <- scale(dat_ancova$difficulty, center=TRUE, scale=FALSE)

@@

# transform data by differencing two consecutive scores, filter for first and second transfer 
library(dplyr)
dat_test1 <- dat %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score)) %>%
         group_by(human_id) %>%
            mutate(diff_score = avg_score - lag(avg_score, default = 0)) %>%
              mutate(learn_phase =c("init RPS","within RPS","transfer 1","within WFG","transfer 2","within MOD"))

>>>>

```{r}
dat1 <- read.csv("data20180719.csv")
```

@@

# transform 'winner' variable in numeric score
dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))

# create a new variable "game.f" as a factor variable of games
dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))

# overall score to pay bonuses 
dat_score <- dat1 %>% 
  group_by(human_id) %>% 
      summarize(overall_score = sum(score))
(avg_bonus <- floor(mean(abs(dat_score$overall_score))))*0.02

#Group data by human_id and calculate mean score per block of each game.
dat2 <- dat1 %>% 
  group_by(human_id,condition,game,block,game.f) %>% 
      summarize(block_score = mean(score))

@@

dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
dat2_6 <- dat_26 %>% 
  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
      summarise(early_score = mean(score))

write.csv(dat2_6,"exp1_early_rounds.csv")

# Check group means and SDs
group_by(dat2_6, game.f) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
group_by(dat2_6, game.f,condition) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
# plot early scores per game 
ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

@@

# including confidence 
#aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
#summary(aov_conf_26)

# (ls4 <- lsmeans(aov_early, "game.f"))
# (summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))

(means.int2 <- lsmeans(aov_early, specs = c("game.f","condition")))
(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","NUM")))
#(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))

@@

# plots overall effect by game :
ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))

@@

```{r}
# adding confidence and difficulty feedback 
datcd <- dat1 %>% 
  group_by(human_id,condition,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))

@@

```{r}
# ANCOVA with confidence as covariate 
dat_ancova <- dat1 %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))
# Centering variables for ANCOVA 
dat_ancova$conf_cen <- scale(dat_ancova$confidence, center=TRUE, scale=FALSE) 
dat_ancova$diff_cen <- scale(dat_ancova$difficulty, center=TRUE, scale=FALSE)

@@

# transform data by differencing two consecutive scores, filter for first and second transfer 
library(dplyr)
dat_test1 <- dat1 %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score)) %>%
         group_by(human_id) %>%
            mutate(diff_score = avg_score - lag(avg_score, default = 0)) %>%
              mutate(learn_phase =c("init RPS","within RPS","transfer 1","within WFG","transfer 2","within MOD"))
